Draft Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-04-20 draftfinalreport_v3.tex
Revised tables NIR mmr

\vspace{5mm} %5mm vertical space
\begin{table}
% latex table generated in R 3.0.2 by xtable 1.7-1 package
% Mon Apr 20 21:01:25 2015
\begin{tabular}{lrrrrrr}
  \hline
 & Df & Deviance & Resid. Df & Resid. Dev & F & Pr($>$F) \\ 
  \hline
NULL &  &  & 59 & 1532.80 &  &  \\ 
  Age & 4 & 1345.17 & 55 & 187.63 & 204.01 & 0.0000 \\ 
  Ethnicity & 3 & 19.88 & 52 & 167.75 & 4.02 & 0.0141 \\ 
  NZDep & 2 & 17.10 & 50 & 150.65 & 5.19 & 0.0102 \\ 
  Age:Ethnicity & 12 & 80.80 & 38 & 69.85 & 4.09 & 0.0004 \\ 
   \hline
\end{tabular}\caption{Significance of different predictor variables for measles risk factors from 2007-2014, estimated using \autoref{eq:reg} and a quasipoisson error structure}
\label{table:anova}
\end{table}

\vspace{5mm} %5mm vertical space
\begin{table}
% latex table generated in R 3.0.2 by xtable 1.7-1 package
% Mon Apr 20 21:01:25 2015
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & -6.1644 & 0.1267 & -48.65 & 0.0000 \\ 
  Age2-4 & -1.0351 & 0.1972 & -5.25 & 0.0000 \\ 
  Age5-17 & -0.9954 & 0.1368 & -7.28 & 0.0000 \\ 
  Age18-24 & -1.7204 & 0.1926 & -8.93 & 0.0000 \\ 
  Age25+ & -3.1697 & 0.1622 & -19.55 & 0.0000 \\ 
  EthnicityAsian & 0.2464 & 0.3168 & 0.78 & 0.4415 \\ 
  EthnicityMaori & 0.2081 & 0.2121 & 0.98 & 0.3327 \\ 
  EthnicityPacific & 1.2200 & 0.2134 & 5.72 & 0.0000 \\ 
  NZDep4-7 & -0.2609 & 0.0948 & -2.75 & 0.0090 \\ 
  NZDep8-10 & -0.3043 & 0.1040 & -2.93 & 0.0058 \\ 
  Age2-4:EthnicityAsian & -2.3148 & 1.3319 & -1.74 & 0.0903 \\ 
  Age5-17:EthnicityAsian & -1.2453 & 0.4566 & -2.73 & 0.0096 \\ 
  Age18-24:EthnicityAsian & -1.0187 & 0.5743 & -1.77 & 0.0841 \\ 
  Age25+:EthnicityAsian & 0.2344 & 0.4298 & 0.55 & 0.5887 \\ 
  Age2-4:EthnicityMaori & -0.1013 & 0.3644 & -0.28 & 0.7826 \\ 
  Age5-17:EthnicityMaori & -0.1032 & 0.2521 & -0.41 & 0.6846 \\ 
  Age18-24:EthnicityMaori & -0.5723 & 0.4409 & -1.30 & 0.2022 \\ 
  Age25+:EthnicityMaori & -1.0349 & 0.5127 & -2.02 & 0.0506 \\ 
  Age2-4:EthnicityPacific & -0.9798 & 0.4676 & -2.10 & 0.0429 \\ 
  Age5-17:EthnicityPacific & -1.5709 & 0.3312 & -4.74 & 0.0000 \\ 
  Age18-24:EthnicityPacific & -1.0354 & 0.5003 & -2.07 & 0.0453 \\ 
  Age25+:EthnicityPacific & -0.6629 & 0.4279 & -1.55 & 0.1296 \\ 
   \hline
\end{tabular}\caption{Summary of the regression model results using \autoref{eq:reg} and a quasipoisson error structure, for measles risk factors for cases from 2007-12 June 2014}
\label{table:regression_riskfactors}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12006[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.9231$&$0.9604$&$0.9457$&$1$&$1$&$318$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2006 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12006}.}
\label{table:tab12006}
\end{table}

\begin{sidewaysfigure}
   \begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2006.pdf}
    \end{center}
    \caption{Proportion of the New Zealand population born in 2006 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab12006} and the supplementary data for details.}
%\end{center}
\label{fig:fig12006}
\end{sidewaysfigure}

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22006[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.8611$&$0.9167$&$0.9029$&$0.9714$&$1.143$&$318$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2006 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22006}.}
\label{table:tab22006}
\end{table}

\begin{sidewaysfigure}
\begin{center}
\includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2006.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2006 vaccinated against measles using MMR2 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab22006} and the supplementary data for details.}
% \end{center}
\label{fig:fig22006}
\end{sidewaysfigure}

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12007[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.9286$&$0.9621$&$0.9499$&$1$&$1$&$324$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2007 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12007}.}
\label{table:tab12007}
\end{table}

\begin{sidewaysfigure}
\begin{center}
\includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2007.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2007 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab12007} and the supplementary data for details.}
% \end{center}
\label{fig:fig12007}
\end{sidewaysfigure}

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22007[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.8592$&$0.9099$&$0.899$&$0.9643$&$1$&$324$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2007 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22007}.}
\label{table:tab22007}
\end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2007.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2007 vaccinated against measles using MMR2 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab22007} and the supplementary data for details.}
% \end{center}
\label{fig:fig22007}
\end{sidewaysfigure}

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12008[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.9365$&$0.971$&$0.9569$&$1$&$1$&$315$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2008 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12008}.}
\label{table:tab12008}
\end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2008.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2008 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab12008} and the supplementary data for details.}
% \end{center}
\label{fig:fig12008}
\end{sidewaysfigure}

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22008[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.8451$&$0.9048$&$0.8908$&$0.9583$&$1$&$315$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2008 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22008}.}
\label{table:tab22008}
\end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2008.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2008 vaccinated against measles using MMR2 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab22008} and the supplementary data for details.}
% \end{center}
\label{fig:fig22008}
\end{sidewaysfigure}

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12009[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.939$&$0.9722$&$0.9575$&$1$&$1$&$324$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2009 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12009}.}
\label{table:tab12009}
\end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2009.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2009 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab12009} and the supplementary data for details.}
%\end{center}
\label{fig:fig12009}
\end{sidewaysfigure}

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22009[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.8302$&$0.8889$&$0.8773$&$0.9444$&$1$&$324$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2009 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22009}.}
\label{table:tab22009}
\end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2009.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2009 vaccinated against measles using MMR2 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab22009} and the supplementary data for details.}
%\end{center}
\label{fig:fig22009}
\end{sidewaysfigure}

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12010[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0.0714$&$0.9326$&$0.9667$&$0.9557$&$1$&$1$&$321$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2010 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12010}.}
\label{table:tab12010}
\end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2010.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2010 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab12010} and the supplementary data for details.}
%\end{center}
\label{fig:fig12010}
\end{sidewaysfigure}

>>>>

\vspace{5mm} %5mm vertical space
\begin{table}
% latex table generated in R 3.0.2 by xtable 1.7-3 package
% Tue Apr 21 10:02:47 2015
\begin{tabular}{lrrrrrr}
  \hline
 & Df & Deviance & Resid. Df & Resid. Dev & F & Pr($>$F) \\ 
  \hline
NULL &  &  & 59 & 1532.80 &  &  \\ 
  Age & 4 & 1345.17 & 55 & 187.63 & 204.01 & 0.0000 \\ 
  Ethnicity & 3 & 19.88 & 52 & 167.75 & 4.02 & 0.0141 \\ 
  NZDep & 2 & 17.10 & 50 & 150.65 & 5.19 & 0.0102 \\ 
  Age:Ethnicity & 12 & 80.80 & 38 & 69.85 & 4.09 & 0.0004 \\ 
   \hline
\end{tabular}\caption{Significance of different predictor variables for measles risk factors from 2007-2014, estimated using \autoref{eq:reg} and a quasipoisson error structure}
\label{table:anova}
\end{table}

\vspace{5mm} %5mm vertical space
\begin{table}
% latex table generated in R 3.0.2 by xtable 1.7-3 package
% Tue Apr 21 10:02:47 2015
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & -6.1644 & 0.1267 & -48.65 & 0.0000 \\ 
  Age2-4 & -1.0351 & 0.1972 & -5.25 & 0.0000 \\ 
  Age5-17 & -0.9954 & 0.1368 & -7.28 & 0.0000 \\ 
  Age18-24 & -1.7204 & 0.1926 & -8.93 & 0.0000 \\ 
  Age25+ & -3.1697 & 0.1622 & -19.55 & 0.0000 \\ 
  EthnicityAsian & 0.2464 & 0.3168 & 0.78 & 0.4415 \\ 
  EthnicityMaori & 0.2081 & 0.2121 & 0.98 & 0.3327 \\ 
  EthnicityPacific & 1.2200 & 0.2134 & 5.72 & 0.0000 \\ 
  NZDep4-7 & -0.2609 & 0.0948 & -2.75 & 0.0090 \\ 
  NZDep8-10 & -0.3043 & 0.1040 & -2.93 & 0.0058 \\ 
  Age2-4:EthnicityAsian & -2.3148 & 1.3319 & -1.74 & 0.0903 \\ 
  Age5-17:EthnicityAsian & -1.2453 & 0.4566 & -2.73 & 0.0096 \\ 
  Age18-24:EthnicityAsian & -1.0187 & 0.5743 & -1.77 & 0.0841 \\ 
  Age25+:EthnicityAsian & 0.2344 & 0.4298 & 0.55 & 0.5887 \\ 
  Age2-4:EthnicityMaori & -0.1013 & 0.3644 & -0.28 & 0.7826 \\ 
  Age5-17:EthnicityMaori & -0.1032 & 0.2521 & -0.41 & 0.6846 \\ 
  Age18-24:EthnicityMaori & -0.5723 & 0.4409 & -1.30 & 0.2022 \\ 
  Age25+:EthnicityMaori & -1.0349 & 0.5127 & -2.02 & 0.0506 \\ 
  Age2-4:EthnicityPacific & -0.9798 & 0.4676 & -2.10 & 0.0429 \\ 
  Age5-17:EthnicityPacific & -1.5709 & 0.3312 & -4.74 & 0.0000 \\ 
  Age18-24:EthnicityPacific & -1.0354 & 0.5003 & -2.07 & 0.0453 \\ 
  Age25+:EthnicityPacific & -0.6629 & 0.4279 & -1.55 & 0.1296 \\ 
   \hline
\end{tabular}\caption{Summary of the regression model results using \autoref{eq:reg} and a quasipoisson error structure, for measles risk factors for cases from 2007-12 June 2014}
\label{table:regression_riskfactors}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(table_nir_mmr, file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{lrrrrrrr}
\hline\hline
\multicolumn{1}{c}{Year}&\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
MMR1 2006&$0.00$&$92.31$&$96.04$&$94.57$&$100.00$&$100.0$&$318$\tabularnewline
MMR2 2006&$0.00$&$86.11$&$91.67$&$90.29$&$ 97.14$&$114.3$&$318$\tabularnewline
MMR1 2007&$0.00$&$92.86$&$96.21$&$94.99$&$100.00$&$100.0$&$324$\tabularnewline
MMR2 2007&$0.00$&$85.92$&$90.99$&$89.90$&$ 96.43$&$100.0$&$324$\tabularnewline
MMR1 2008&$0.00$&$93.65$&$97.10$&$95.69$&$100.00$&$100.0$&$315$\tabularnewline
MMR2 2008&$0.00$&$84.51$&$90.48$&$89.08$&$ 95.83$&$100.0$&$315$\tabularnewline
MMR1 2009&$0.00$&$93.90$&$97.22$&$95.75$&$100.00$&$100.0$&$324$\tabularnewline
MMR2 2009&$0.00$&$83.02$&$88.89$&$87.73$&$ 94.44$&$100.0$&$324$\tabularnewline
MMR1 2010&$7.14$&$93.26$&$96.67$&$95.57$&$100.00$&$100.0$&$321$\tabularnewline
MMR2 2010&$0.00$&$62.50$&$70.59$&$69.74$&$ 77.91$&$100.0$&$321$\tabularnewline
MMR1 2011&$0.00$&$92.86$&$96.43$&$94.92$&$100.00$&$100.0$&$326$\tabularnewline
MMR2 2011&$0.00$&$ 0.00$&$ 3.45$&$ 6.06$&$  8.93$&$100.0$&$326$\tabularnewline
MMR1 2012&$0.00$&$93.33$&$96.67$&$95.27$&$100.00$&$100.0$&$331$\tabularnewline
MMR2 2012&$0.00$&$ 0.00$&$ 0.41$&$ 4.03$&$  4.76$&$100.0$&$331$\tabularnewline
MMR1 2013&$0.00$&$55.56$&$63.33$&$62.76$&$ 70.00$&$100.0$&$331$\tabularnewline
MMR2 2013&$0.00$&$ 0.00$&$ 0.00$&$ 2.17$&$  2.63$&$100.0$&$331$\tabularnewline
MMR1 2014&$0.00$&$ 0.00$&$ 0.00$&$ 0.88$&$  0.00$&$100.0$&$334$\tabularnewline
MMR2 2014&$0.00$&$ 0.00$&$ 0.00$&$ 0.67$&$  0.00$&$100.0$&$334$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2006--2014 birth cohorts vaccinated against measles-mumps-rubella (MMR) dose 1 and MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12006}, \autoref{fig:fig22006}, \autoref{fig:fig12007}, \autoref{fig:fig22007}, \autoref{fig:fig12008}, \autoref{fig:fig22008}, \autoref{fig:fig12009}, \autoref{fig:fig22009}, \autoref{fig:fig12010}, \autoref{fig:fig22010}, \autoref{fig:fig12011}, \autoref{fig:fig22011}, \autoref{fig:fig12012}, \autoref{fig:fig22012}, \autoref{fig:fig12013}, \autoref{fig:fig22013}, \autoref{fig:fig12014}, and \autoref{fig:fig22014}.}
\label{table:tab_mmr_nir}
\end{table}

\begin{sidewaysfigure}
   \begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2006.pdf}
    \end{center}
    \caption{Proportion of the New Zealand population born in 2006 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig12006}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22006)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22006[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2006 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22006}.}
% \label{table:tab22006}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
\includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2006.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2006 vaccinated against measles using MMR2 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig22006}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12007)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12007[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2007 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12007}.}
% \label{table:tab12007}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
\includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2007.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2007 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig12007}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22007)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22007[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2007 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22007}.}
% \label{table:tab22007}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2007.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2007 vaccinated against measles using MMR2 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig22007}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12008)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12008[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2008 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12008}.}
% \label{table:tab12008}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2008.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2008 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig12008}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22008)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22008[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2008 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22008}.}
% \label{table:tab22008}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2008.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2008 vaccinated against measles using MMR2 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig22008}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12009)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12009[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2009 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12009}.}
% \label{table:tab12009}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2009.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2009 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig12009}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22009)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22009[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2009 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22009}.}
% \label{table:tab22009}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2009.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2009 vaccinated against measles using MMR2 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig22009}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12010)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12010[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2010 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12010}.}
% \label{table:tab12010}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2010.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2010 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig12010}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22010)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22010[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2010 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22010}.}
% \label{table:tab22010}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2010.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2010 vaccinated against measles using MMR2 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig22010}
\end{sidewaysfigure}
